Covariate analysis of ROSMAP RNASeq with Quantile and SVA normalisation

### 2016-09-07 code/Rmd/ROSMAP_RNASeq_Qntl_SVA.Rmd
Minor fix

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file

@@

library(ggplot2)
library(reshape2)
library(limma)
library(Biobase)
library(gplots)
library(WGCNA)
library(psych)
library(edgeR)
library(biomaRt)
library(Rcolorbrewer)

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache = FALSE}
## It is assumed your working directory is where this file

@@

library(ggplot2)
library(reshape2)
library(limma)
library(Biobase)
library(gplots)
library(WGCNA)
library(psych)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
